---
title: "Homework_9"
author: "Maha Siva"
date: "2025-04-17"
output: pdf_document
---

Github Link: https://github.com/MahaSiva1/SDS_HW_9



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(moderndive)
library(effectsize)

```

# Question 1 
```{r, echo=FALSE}
solder <- read.csv("/Users/mahasivasubramanian/Desktop/SDS315/solder.csv")


```

### Part A

```{r, echo=FALSE}
library(ggplot2)
ggplot(solder) + geom_boxplot(aes(x=Opening, y=skips)) + labs(x="Opening Size", y="Number of Skips", title="Opening Size vs. Number of Skips") 

```
In the figure above, we see a possible correlation between opening size and number of skips. A small opening appears to have more number of skips while a large opening seems to have lower number of skips. 


```{r, echo=FALSE}
ggplot(solder) + geom_boxplot(aes(x=Solder, y=skips)) + labs(x="Solder", y="Number of Skips", title="Solder vs Number of Skips") 
```
In the figure above we see a possible correlation between the thickness of the alloy and number of skips. A thin solder seems to have greater number of skips than a thick solder.

### Part B 

```{r, echo=FALSE, include=FALSE}
model_skip2 = lm(skips ~ Solder + Opening + Solder:Opening, data=solder)
confint(model_skip2, level = .95)



```
```{r, echo=FALSE}
get_regression_table(model_skip2, conf.level = 0.95, digits=2)

```

### Part C 

interpretation 
* the baseline number of skips skips that are large and thick is .39. 
* the main effect of thin solder is 2.28 units. this is the effect of thin solder in isolation. 
* the main effect of medium opening is 2.41. this is the effect of medium size opening on skips in isolation 
* the main effect of small opening is 5.12. this is the effect of small opening on skips in isolation. 
* the interaction effect for thin solder and medium size opening is -.74. In other words, when we have both solder thin and a medium opening would produce 0.74 less skips that what we would have expected from summing the individual “isolated” effects of the two variables.
* the interaction effect for the thin solder and a small opening is 9.65. In other words, when we have both solder thin and small opening we would have 9.65 greater than what you expect from summing the individual “isolated” effects of the two variables.

### Part D 
If At&T was looking for the combination of opening size and Solder thickness, I would recommend a large opening size with a thick solder. This is the baseline group for our regression model and its value of 0.393 is the lowest value for number of skips, especially when comparing to all of the interaction effects and adding of all terms. 

# Question 2 

```{r, echo=FALSE}
groceries <- read.csv("/Users/mahasivasubramanian/Desktop/SDS315/groceries.csv")

```

```{r, echo=FALSE}

groceries %>%
  group_by(Store) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(Store, mean_price), y = mean_price)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
  labs(x = "Store", y = "Average Price", title = "Average Price of Products by Store")
```
This graph displays all of the stores in our data set and the average price of the products in those stores. We see that Whole Foods has the greatest price of product and Fiesta has the lowest average price of Product.  

### Part B 
```{r, echo=FALSE, fig.width=8, fig.height=12}
groceries %>%
  group_by(Product) %>%
  summarize(num_stores = n_distinct(Store)) %>%
  ggplot(aes(x=Product, y=num_stores)) + geom_bar(stat = "identity", fill = "darkseagreen") + labs(x="Number of Stores", y="Product", title="Number of Stores vs Product") +
  coord_flip() 



```

### Part C 
```{r, include=FALSE, echo=FALSE}
lm_groceries = lm(Price ~ Product + Type, data=groceries)
confint(lm_groceries, level = 0.95)
coef(lm_groceries)
get_regression_table(lm_groceries, conf.level = 0.95, digits=2)

```

Compared with ordinary grocery stores, convenience stores charge somewhere between .41 and .92 dollars more for the same product. 

### Part D 
```{r, echo=FALSE, include=FALSE}

lm_groceries1 = lm(Price ~ Product + Store, data=groceries)
confint(lm_groceries1, level = 0.95)
get_regression_table(lm_groceries1, conf.level = 0.95, digits=2)

```

```{r, echo=FALSE, include=FALSE}
store_effects <- get_regression_table(lm_groceries1, conf.level = 0.95, digits = 2) %>%
  filter(grepl("^Store", term)) %>%
  arrange(estimate)

# Lowest priced stores
head(store_effects, 2)

# Highest priced stores
tail(store_effects, 2)

```
One of the stores with the lowest estimated prices are Walmart with prices that average $.99  less than the baseline store, with a confidence interval of [-$1.45, -$0.53]. Another store with low estimate prices is Kriger Fresh Fare with a estimate of $-.90 and a confidence interval of [-$1.36, -$.44]. 

The stores with the greatest estimated prices are Wheatesville Food Co-op and Whole Foods. Wheatsville has a estimate of .29 with a 95% confidence interval of [-$0.06, $0.64]. Whole foods has a estimate of 0.36 with a 95% confidence interval of [$0.02, $0.71]. 

### Part E

From the model, it can be seen that H-E-B has a coefficient of -0.65 (95% Cl: [-0.95, -0.35]) and Central Market has a coefficient of -0.57 (95% el: [-0.92, -0.23]). Therefore the estimated price difference between Central Market and H-E-B is 0.08, meaning that central market charges slightly more for the same product. 


### Part F 
```{r, echo=FALSE, include=FALSE}
groceries <- groceries %>% 
  mutate(Income10k = round(Income / 10000, 0))

groceries2 = lm(Price~Product + Income10k, data=groceries)
get_regression_table(groceries2, conf.level=.95, digits=3)

standardize_parameters(groceries2)

```

Based on the sign of the Income10k coefficient, consumers in poorer ZIP codes seem to pay more for the same product, on average. The coefficient is negative, meaning that as income increases, the expected price decreases slightly. A one-standard deviation increase in the income of a ZIP code seems to be associated with a 0.04 standard-deviation decrease in the price that consumers in that ZIP code expect to pay for the same product.



# Problem 3 


### A - ZIP codes with a higher percentage of minority residents tend to have more FAIR policies per 100 housing units.

### TRUE

This statement is true. According to Figure A, the model has a R-squared value of .5163 which indicates that 51.6% of the variability in product prices can be explained by the model which shows that it is a moderately strong model. In addition, the slope for minority is [.009, .018]. As 0 is not included in the confidence interval, there it is statistically significant.


### B. The evidence suggests an interaction effect between minority percentage and the age of the housing stock in the way that these two variables are related to the number of FAIR policies in a ZIP code. 

### UNDECIDABLE

The model does not include an interaction term for age and minority. In order for us to more accurately determine for an interaction, model A would have to include an interaction effect, for example:model_A <- lm(policies ~ minority + age, data = redlining) and then using the slope and the interval, we can determine the validity the interaction effect. 

### C. The relationship between minority percentage and number of FAIR policies per 100 housing units is stronger in high-fire-risk ZIP codes than in low-fire-risk ZIP codes. 

### UNDECIDABLE

This statement is undecidable. According to figure C1, the slope of both the high fire risk and the low fire risk are very similar and if we look at the model C the interaction effect of minority groups and fire risk low has a confidence interval of [-0.012, 0.01]. Because this interval includes 0 in its interval we can not assume statistical significance. 

### D. Even without controlling for any other variables, income “explains away” all the association between minority percentage and FAIR policy uptake. 

### FALSE 

According to model D, with minority + income, the coefficient of the minority is .01 verus in model A, the minority coefficient is .014. Therefore in model D, the income explains some of the association between minority perctange and policy uptake but there is still correlation between minority percentage and policies which is also proven by 95% confidence interval [0.004, 0.015] does not include 0. 

### E. Minority percentage and number of FAIR policies are still associated at the ZIP code level, even after controlling for income, fire risk, and housing age. 

### TRUE 

In model E, after controlling for all the variables listed above such as income, fire risk, housing age. The coefficient for minority is estimate =.008 and p =.006 which indicates statistically significance. Therefore minority percentage remains a significant predictor of FAIR policies. 




